TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-08-13 paper/draft.tex
extension sample

The physical parameter sample consists of 87 sources with reference labels distributed over $2859 <T_{\rm eff} < 4131$K, and $-0.48 <$ [Fe/H] $< 0.49$, 41 sources of which are drawn from \citealt{Mann:2015} (hereafter M15), and 46 of which are part of an previously unpublished extension sample to M15 analyzed using similar data and identical techniques to M15. The M15 catalog in total contains 183 sources and the extension sample another 500 primarily selected from the proper-motion selected CONCH-SHELL \citep{Gaidos:2013} M dwarf catalog. All targets have low-res optical spectra from the SNIFS specgrograph \citep{Lantz:2004} and infrared spectra taken with the SpeX Spectograph \citep{Rayner:2003}, which have been combined to estaimte largely empirical bolometric fluxes. Effective temperatures have been estimated by comparing the SNIFS spectra to BT-SETTL atmospheric models \citep{Allard:2011}. A subsample of 29 sources with measured angular diameters from long-baseline optical interferometry \citep{Boyajian:2012} are used to calibrate the model comparison, including masking of spectral regions poorly reproduced by the model spectra \citep{Mann:2013c}. Based on difference between assigned \teff\ values and those from angular diameters, absolute uncertainty on \teff\ is esitmated to be 60K in \teff, although the relative uncertainty is likely a factor of $\simeq$2 better.
%AWM: I realized I've never actaully sat down and rigorously measured the relative Teff uncertainty. The results from the Cannon actually suggest ~30 is not bad. I just did some quick tests, and I'm not prepared to put an absolute number on it. A \simeq 30 here should be safeish.

>>>>

The physical parameter sample consists of 87 sources with reference labels distributed over $2859 <T_{\rm eff} < 4131$K, and $-0.48 <$ [Fe/H] $< 0.49$, 41 sources of which are drawn from \citealt{Mann:2015} (hereafter M15), and 46 of which are part of an previously unpublished extension sample to M15 analyzed using similar data and identical techniques to M15. The major difference between the extension sample is that the sample had lower-quality or no parallaxes (prior to Gaia data) and hence were omitted from the M15 study and were less vetted for binarity than the M15 sample.

The M15 catalog in total contains 183 sources and the extension sample another 500 stars, both primarily selected from the proper-motion selected CONCH-SHELL \citep{Gaidos:2013} M dwarf catalog. All targets have low-res optical spectra from the SNIFS specgrograph \citep{Lantz:2004} and infrared spectra taken with the SpeX Spectograph \citep{Rayner:2003}, which have been combined to estaimte largely empirical bolometric fluxes. Effective temperatures have been estimated by comparing the SNIFS spectra to BT-SETTL atmospheric models \citep{Allard:2011}. A subsample of 29 sources with measured angular diameters from long-baseline optical interferometry \citep{Boyajian:2012} are used to calibrate the model comparison, including masking of spectral regions poorly reproduced by the model spectra \citep{Mann:2013c}. Based on difference between assigned \teff\ values and those from angular diameters, absolute uncertainty on \teff\ is esitmated to be 60K in \teff, although the relative uncertainty is likely a factor of $\simeq$2 better.
%AWM: I realized I've never actaully sat down and rigorously measured the relative Teff uncertainty. The results from the Cannon actually suggest ~30 is not bad. I just did some quick tests, and I'm not prepared to put an absolute number on it. A \simeq 30 here should be safeish.
